\section{Project Plan}
Below is a high-level project plan. The plan is broken down into subsequent phases
(loosely following the Unified Process, see e.g. \cite{kruchten:rup}) that will be
executed sequentially; within each phase there is a summary of the tasks to carry 
out to reach the completion of that phase. Tasks within each phase may be carried 
out concurrently as needed. Milestones track project progress by specifying what is
the expected outcome at a point in time and how long it is expected to take---i.e. 
a time estimate for the completion of all the tasks leading up to that 
milestone.\footnote{Each task was estimated separately using PERT three-point 
estimation: Call $b$, $w$, $l$ the best, worst, likely task completion time, 
respectively; we took the expected completion time $t$ to be: $t = \frac{b + 4l + w}{6}$. 
Then we summed up expected completion times for the tasks leading up to that milestone.
}

\subsection{Inception}

\subsubsection*{Goals}
Initiate project and prepare ground for development. 

\subsubsection*{Tasks} 
Establish vision, scope and justification for project. 
Gather key requirements and identify risks.
Familiarise with OMERO platform.
Build development, test, and server virtual machines.

\subsubsection*{Milestone (M1)}
All inception tasks completed. Virtual machines ready for development cycles.
Project approved by CNRS steering committee.
\emph{Expected Completion Time}: 15 days.

\subsection{Elaboration}

\subsubsection*{Goals}
Establish and validate solution architecture. 

\subsubsection*{Tasks} 
Analyse requirements.
Study candidate solutions.
Attend OMERO conference to discuss plans and development options.
Select solution architecture and produce project plan.
Write project overview document (only draft needed).
Familiarise with ISO certification procedure and Redmine project management.

\subsubsection*{Milestone (M2)}
All elaboration tasks completed. Project managed in Redmine and ready to be audited.
\emph{Expected Completion Time}: 24 days.

\subsection{Construction}

\subsubsection*{Goals}
Implement system features. 

\subsubsection*{Tasks} 
Develop initial prototype: Import Proxy ICE interface; ICE servant and client; Import
Plugin button and asynchronous call to the proxy.
Develop unit and integration tests. 
Have small group of end users test and evaluate product; steer further development
according to received feedback.

\subsubsection*{Milestone (M3)}
Prototype is stable and other system features can be added.
\emph{Expected Completion Time}: 16 days. %% from July 1 to 23

\subsubsection*{Tasks} 
Evolve prototype into deliverable product by implementing: write-ahead log, locking,
notifications, configuration, server control interface, control script.
Develop unit and integration tests.
Write developer documentation.
Build pre-production environment to deploy and test deliverable.
End to end testing.
Load testing.

\subsubsection*{Milestone (M4)}
All construction tasks completed. All system features implemented. System fully tested
and ready for deployment.
\emph{Expected Completion Time}: 27 days. %% from July 24 to August 31

\subsection{Transition}

\subsubsection*{Goals}
Deploy system to production environment. Refine product to incorporate any feedback
received from end users.

\subsubsection*{Tasks} 
Conduct pilot deployment using small group of end users to test and evaluate product
in production environment: install OMERO Java client on selected machines, set up 
Import Proxy service, assign permissions, configure admin mailbox.
Monitor running system and fix any issues.
Collect feedback from end users and refine product as needed.
Prepare end-user training materials.
Write end-user documentation. 

\subsubsection*{Milestone (M5)}
System is running smoothly in a controlled production environment. Any issues have 
been fixed and end-user feedback incorporated into product. System is ready for 
deployment to all MRI target machines.
\emph{Expected Completion Time}: 19 days. %% from September 1 to 25

\subsubsection*{Tasks}
Deploy system to all MRI target machines.
Monitor deployment and fix any issues.

\subsubsection*{Milestone (M6)}
All transition tasks completed. System is running smoothly in production environment. 
Project ends and product enters maintenance phase.
\emph{Expected Completion Time}: 5 days. %% from September 28 to October 2


